---
title: "Assignment 1"
editor_options: 
  markdown: 
    wrap: 72
---

# A word about R markdown

The assignments for our online R training course will all take the form
of R markdown documents like this one. These are files ending in '.Rmd'
that combine R code blocks with plain text, such as this paragraph that
you're reading now.

To run the R code blocks you need to have this R markdown file open in
RStudio. If you're reading this in RStudio right now then all is good
and well. If not, please start RStudio and open this file using the
'Open File...' option from the 'File' menu.

Also, it might be a good idea to create a folder on your computer in
which to store this assignment and the assignments for the coming weeks,
along with some data files that will be provided for use in some of the
future assignments.

In these assignments we will describe what we're asking you to do in
some plain text which will be followed by an empty code block in which
you will write the R commands as your answers to the exercise.

Here's an example. Suppose we ask you to add two numbers, 34 and 102,
together. The empty code block where you would carry out this
calculation would look like this:

```{r}

```

It should appear as a grey box with three small grey and green icons at
the top on the right hand side.

You can fill in the answer as follows:

```{r}
34 + 102
```

You can add extra lines as necessary by hitting the 'Return' key.

Now to run this command you can click on the green arrow or triangle
icon, the one that is furthest right and points right-ward. If you hover
over this icon, you should get a tool tip saying 'Run current chunk'.
Click on this and see what happens.

You should see the answer printed just below the code block, much as you
would have seen in the Console prefixed with the (hopefully) now
familiar '[1]' that indicates this is a vector and you're looking at the
first element.

In this first assignment, we are deliberately going to restrict our use
of the markdown format to just a few features. You'll notice the header
containing the title, author and date and also section headings starting
with '\#'. Other than that we will just use sections of plain text and R
code blocks or chunks as they're more properly known.

As we go through successive assignments during the course, we'll
introduce more features of R markdown. It's a great way of writing R
code for analyzing and visualizing your data that lets you present your
work in beautiful, self-describing reports, a sure-fire way to impress
your group leader and colleagues alike.

R markdown is really easy to learn and will let you do a lot of cool
things. Our course website was created with R markdown documents that
are not that much more complicated than the file you're reading right
now for this assignment.

Now on with this week's exercises.

# Using R as a calculator

1.  Convert the following temperatures given in degrees Fahrenheit to
    Celsius: 45, 96, 451

```{r}

```

Hint: just do what you'd normally do if you can't remember the formula
for converting between Celsius and Fahrenheit (Google in my case).

If you like, you can experiment with getting your R code right in the
Console window first and then copy it into the code chunk above when
you're happy with it. It's not crucial and getting it wrong in the R
markdown is no big deal. You can always fix any problems (the most
likely being forgetting to use parentheses or brackets in the right
place) and re-run your code using the green arrow/triangle icon.

Check you've got the right answer by finding a web page with a handy
conversion tool.

2.  Similarly, convert the following temperatures in degrees Celsius to
    Fahrenheit: -65, 100, 20

```{r}

```

# Practice with Vectors

3.  t is interested in the number of dogs on her block. She notes that
    the first house has one dog, the second house has no dogs, the third
    house has 4 dogs, and the fourth house has one dog. Create a vector
    that represents these observations named dogs.

    ```{r}

    ```

4.  It turns out that the scientist was mistaken. The third house
    actually had 5 dogs (the fifth one was hiding in the backyard. Edit
    the vector to reflect the new observations

    ```{r}

    ```
