```{r initiatePackages, message=FALSE}
## you can add more, or change...these are suggestions
library(tidyverse)
library(readr)
library(dplyr)
library(ggplot2)
library(tidyr)
```

**The following questions involve an outside dataset.**

We will be working with a dataset from the "Kaggle" website, which hosts competitions for prediction and machine learning. More details on this dataset are here: <https://www.kaggle.com/c/DontGetKicked/overview/background>.

5\. Bring the dataset into R. The dataset is located at: <https://jhudatascience.org/intro_to_r/data/kaggleCarAuction.csv>. You can use the link, download it, or use whatever method you like for getting the file. Once you get the file, read the dataset in using `read_csv()` and assign it the name `cars`.

```{r}
#
```

6\. Import the data "dictionary" from <https://jhudatascience.org/intro_to_r/data/Carvana_Data_Dictionary_formatted.txt>. Use the `read_tsv()` function and assign it the name "key".

```{r}
#
```

7\. You should now be ready to work with the "cars" dataset.

(a) Preview the data so that you can see the names of the columns. There are several possible functions to do this.
(b) Determine the class of the first three columns using `str()`. Write your answer as a comment inside the R chunk below.

```{r}
#
```

8\. How many cars (rows) are in the dataset? How many variables (columns) are recorded for each car?

```{r}
#
```

9\. Filter out (i.e., remove) any vehicles that cost less than or equal to \$5000 ("VehBCost") or that have missing values. Replace the original "cars" object by reassigning the new filtered dataset to "cars". How many vehicles are left after filtering?

**Hint:** The `filter()` function also removes missing values.

```{r}
#
```

10\. From this point on, work with the filtered "cars" dataset from the above question. Given the average car loan today is 70 months, create a new variable (column) called "MonthlyPrice" that shows the monthly cost for each car (Divide "VehBCost" by 70). Check to make sure the new column is there.

**Hint:** use the `mutate()` function.

```{r}
#
```

F. Knit your document into a report.

You use the knit button to do this. Make sure all your code is working first!
